### 2013-09-09 doc/dissertation/document/chapters/conclusion/conclusion.tex
adding Prof Sovinec corrections

\subsubsection{Physics and PDE-based Preconditioners}
Studies should be considered for physics or PDE-based preconditioners
for linear systems that produce a reduced-order model of the original
system to which the Monte Carlo method may be applied. As the Monte
Carlo method serves to construct the solution correction vector in the
MCSA method, the Monte Carlo method may be applied to a reduced-order
physics or PDE-based system that captures the essence of the original
system and still allows for acceleration of the iterative
procedure. By reducing the order of the system, we are effectively
generating a Monte Carlo problem within MCSA in which the linear
operator is either more sparse, has a better-conditioned eigenvalue
spectrum, or both. The reduced domain approximation has shown that a
purely algebraic strategy for reducing the order of the Monte Carlo
problem can result in improved overall timing performance due to
increased sparsity at the cost of iterative performance as a result of
loss of information. A more well informed strategy for order reduction
via either an intelligent simplification of the PDEs that describe the
system or a simplification of the physics involved may prove to be a
more effective strategy.

>>>>

\subsubsection{Physics and PDE-based Preconditioners}
Studies should be considered for physics or PDE-based preconditioners
for linear systems that produce a reduced-order model of the original
system to which the Monte Carlo method may be applied. As the Monte
Carlo method serves to construct the solution correction vector in the
MCSA method, the Monte Carlo method may be applied to a reduced-order
physics or PDE-based system that captures the essence of the original
system and still allows for acceleration of the iterative
procedure. By reducing the order of the system, we are effectively
generating a Monte Carlo problem within MCSA in which the linear
operator is either more sparse, has a better-conditioned eigenvalue
spectrum, or both. In addition, the reduced domain approximation has
shown that a purely algebraic strategy for reducing the order of the
Monte Carlo problem can result in improved overall timing performance
due to increased sparsity at the cost of iterative performance as a
result of loss of information. A more well informed strategy for order
reduction via either an intelligent simplification of the PDEs that
describe the system or a simplification of the physics involved may
prove to be a more effective strategy. In turn, this reduction of
order strategy for the Monte Carlo problem also potentially simplifies
the preconditioning strategy with less sophisticated algebraic
techniques needed for better conditioned approximations of the Monte
Carlo problem.

### 2013-09-09 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
adding Prof Sovinec corrections

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/convection_isotherms.png}
  \end{center}
  \caption{\textbf{Isotherms from solution to the thermal convection
        cavity problem.} \textit{Top left: Ra = \sn{1}{3}; Top right:
        Ra = \sn{1}{4}; Bottom left: Ra = \sn{1}{5}; Bottom left: Ra =
        \sn{1}{6}. Isotherms on unit temperature scale from 0 to 1
        with 10 uniformly spaced curves for each calculation.}}
  \label{fig:convection_isotherms}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/driven_velocity_isocurves.png}
  \end{center}
  \caption{\textbf{Velocity magnitude isocurves from solution to the
      lid driven cavity problem.} \textit{Top left: Re = 100; Top
      right: Re= 300; Bottom left: Re = 500; Bottom left: Re =
      700. Isocurves on unit velocity scale from 0 to 1 with 20
      uniformly spaced curves for each calculation.}}
  \label{fig:driven_velocity_isocurves}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/step_velocity_isocurves.png}
  \end{center}
  \caption{\textbf{Velocity magnitude isocurves from solution to the
      backward facing step problem.} \textit{From top to bottom: Re =
      200, Re = 300, Re = 400, Re = 500. Isocurves on unit velocity
      scale from 0 to 1 with 20 uniformly spaced curves for each
      calculation. The depression forming in the upper right portion
      of visible flow is the second vortex.}}
  \label{fig:step_velocity_isocurves}
\end{figure}

>>>>

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/convection_isotherms.png}
  \end{center}
  \caption{\textbf{Isotherms from solution to the thermal convection
      cavity problem.} \textit{Top left: Ra = \sn{1}{3}; Top right: Ra
      = \sn{1}{4}; Bottom left: Ra = \sn{1}{5}; Bottom left: Ra =
      \sn{1}{6}. Isotherms on unit temperature scale from 0 to 1 with
      10 uniformly spaced curves for each calculation. These results
      were computed with the Drekar fluid code and FANM.}}
  \label{fig:convection_isotherms}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/driven_velocity_isocurves.png}
  \end{center}
  \caption{\textbf{Velocity magnitude isocurves from solution to the
      lid driven cavity problem.} \textit{Top left: Re = 100; Top
      right: Re= 300; Bottom left: Re = 500; Bottom left: Re =
      700. Isocurves on unit velocity scale from 0 to 1 with 20
      uniformly spaced curves for each calculation. These results were
      computed with the Drekar fluid code and FANM.}}
  \label{fig:driven_velocity_isocurves}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/step_velocity_isocurves.png}
  \end{center}
  \caption{\textbf{Velocity magnitude isocurves from solution to the
      backward facing step problem.} \textit{From top to bottom: Re =
      200, Re = 300, Re = 400, Re = 500. Isocurves on unit velocity
      scale from 0 to 1 with 20 uniformly spaced curves for each
      calculation. The depression forming in the upper right portion
      of visible flow is the second vortex. These results were
      computed with the Drekar fluid code and FANM.}}
  \label{fig:step_velocity_isocurves}
\end{figure}
